\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/discussion.tex
Update impact

\subsection{Impact}

>>>>

\subsection{Impact}
%\shuqing{Left after experiment to finish. Will discuss from different modes and application scenarios.}
The USB protocol is used widely as introduced in preceding sections.
As the technologies develops rapidly, more and more devices will be equipped with USB-C capabilities, which makes \tool more influential.
Due to the neglection to check the security of plugged-in USB devices of non-professional users, \tool can be hardly detected by them while attacks are performing.
The popularity and universality of public USB devices, including sharing power banks, even increase such risks.
What's more, \tool provides a better way for traditional BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as interacting with user interface, as well as control the consequences of their attacks.
In summary, \tool can be applied in various application scenarios and brings rather huge impacts.
